\documentclass[a4paper,11pt]{article}
\usepackage[a4paper,margin=2.5cm]{geometry} % adjust margins
\usepackage{mathtools}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{import}
\usepackage{example}
\usepackage{makeidx}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\makeindex

\begin{document}

% Title page
\begin{titlepage}
\vbox{ }

\vbox{ }

\begin{center}
% Upper part of the page
\textsc{\LARGE DRP Türkiye 2025}\\[1.5cm]

\vbox{ }
% Title
{ \huge \bfseries Introduction to Code Based Cryptography}\\[0.5cm]
{\large June-August, 2025}\\[0.5cm]
% Author and supervisor
\begin{minipage}{0.5\textwidth}
\begin{flushleft} \large
\emph{Mentees:}\\
Ronahi Haykır\\ 
Fatemeh Gholami Ghahderijani 
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Mentor:} \\
Dr. Yağmur Çakıroğlu\\
\end{flushright}
\end{minipage}
\\[2cm]
% Abstract
\begin{abstract}
dotdotdot    
\end{abstract}

\vfill
% Bottom of the page
\end{center}
\end{titlepage}

\thispagestyle{empty}
\newpage
\null
\thispagestyle{empty}
\newpage

% Contents
\tableofcontents

\thispagestyle{empty}
\newpage
\null
\thispagestyle{empty}
\newpage

\section{Introduction}
Code-based cryptography is one of the main candidates of post-quantum cryptography, that is to prevent the quantum computers to solve an integer factorization or the discrete logarithm problem over an elliptic curve or over a finite field. It is using hard problems from the algebraic coding theory. The problems usually contain decoding a random linear code which are NP-hard.

We will not cover post-quantum cryptography. Our aim is to equip the reader with a general knowledge about the algebraic coding theory and code-based cryptography. The first section introduces the general terminology and important varieties of codes.

\section{Algebraic Coding Theory}

\subsection{Basics on Hamming-Metric Codes}

\begin{definition}
hamming codes, hamming weight/distance etc.    
\end{definition}

\subsection{Generalized Reed-Solomon Codes}
\subsection{Goppa Codes}
\subsection{Cyclic Codes}
\subsection{Reed-Muller Codes}
\subsection{Rank-Metric Codes}
\subsection{Gabidulin Codes}
\subsection{Code Equivalence}
\subsection{Restricted Errors}

\section{Cryptography}

\subsection{Public-Key Encryption}
\subsection{Key-Encapsulation Mechanisms}
\subsection{Digital Signature Schemes}
\subsection{Fiat-Shamir Transform}

\section{Code-Based Public-Key Encryption Frameworks}

\subsection{McEliece Framework}
\subsection{Niederreiter Framework}

% References
\import{./}{bibliography.tex}
\end{document}
